---
title: "Human-Plant Coevolution model"
author: "Andreas Angourakis & Jonàs Alcaina"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, # hide code and messages
                      cache=TRUE, autodep=TRUE) 
source("library/hpModel.run.R")
source("library/hpModel.exploration.R")
source("library/hpModel.plot.R")
require(reshape2)
require(ggplot2)
require(scales)

run.table <- function(run.result)
{
  run.parnames <- names(run.result$PARS)
  run.parvalues <- c()
  for (i in 1:length(run.result$PARS))
  {
    run.parvalues <- c(run.parvalues, run.result$PARS[[i]])
  }
  knitr::kable(cbind(run.parnames, run.parvalues), col.names = c("parameter", "values"))
}

exp.table <- function(exp.results)
{
  exp.parnames <- c()
  exp.values <- c()
  for (i in 1:17)
  {
    exp.parnames <- c(exp.parnames, names(exp.results)[i])
    value <- levels(factor(exp.results[[i]]))
    if (length(value) > 1) 
    {
      value <- as.numeric(as.character(value))
      value <- paste(min(value), "-", max(value), "(sample=", length(value), ")")
    }
    exp.values <- c(exp.values, value)
  }
  knitr::kable(cbind(exp.parnames, exp.values), col.names = c("parameter", "values"))
}
```


**_Parameters_**

 Abbreviation     | Description
 ---------------- | ---------------------
 `r.h`, `r.p`     | intrinsic growth rates for human and plant populations
 `max.h`          | utility per unit of other resources to humans of type 1 (population of type 1 that can be sustained by resources independent of HP relationship)
 `max.p`          | utility per unit of non-anthropic space to type 1 plants
 `Um.ph`          | utility per unit **of** type N plants **to** type N humans 
 `Um.hp`          | utility per unit **of** type N humans **to** type N plants
 `n.h`, `n.p`     | number of phenotypes of humans and plants
 `v.h`, `v.p`     | level of undirected variation in humans and plants
 `iniH`, `iniP`   | initial populations of humans and plants
 `Ump.ph`         | proportion of utility to humans per unit of type 1 plants **less** than type N
 `Ump.hp`         | proportion of utility to plants per unit of type 1 humans **less** than type N
 `Kmp.h`          | proportion of utility per unit of other resources gained by type N humans **less** than type 1
 `Kmp.p`          | proportion of utility per unit of non-anthropic space gained by type N plants **less** than type 1
 `MaxArea`        | maximum contiguous area to be used by plants


```{r child = '1_singleRunPlots.Rmd'}
```

```{r child = '2_oneParameterExplorationPlots.Rmd'}
```

```{r child = '3_twoParameterExplorationPlots.Rmd'}
```

```{r child = '4_fourParameterExplorationPlots.Rmd'}
```
